\subsection{Experiment type} A quantitative experiment is proposed to validate the hypotheses of this study. Field tests, combined with limited laboratory tests are conducted. Screen and event records are acquired per user.

\subsection{Participant sourcing} 
This study includes participants attained through several sources:
\begin{itemize}
	\item{Local university:} On-site supervised experiments were conducted on a limited scale to facilitate a clean sample of participants and uncover problems during the study
	
	\item{Local workplace:} On-site semi-supervised experiments are conducted on a limited scale in Berlin area in Germany to facilitate a more diverse sample while keeping controlled environment conditions, similar to university experiments.
	
	\item{Social media:} Remote participants are invited to participate in unsupervised experiments on their own. Channels such as social media, interest groups and university mailing lists are used.
	
	\item{Mechanical turk:} MTurk is one of popuar web services to source participants. Previous research has shown that it can be considered a reliable platform for conducting objective studies. MTurk participants receive monetary compensation for participation \cite{Buhrmester2011a}. Mturk participants are excluded from motivation with a chance on winning a voucher prize (they do not see the field and information box about it), instead regular participant reward through MTurk is used. For this study participants received a monetary reward ranging from 0.69 USD to 2.10 USD. The mean time to complete the experiment comes at about eighteen minutes across MTurk users. 
%	The time is specified as it may have an effect on motivation.
	
\end{itemize}

Local and social media experiments provided additional motivation of participation with the promise of a chance to win a 20 Euro Amazon-voucher.